Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-07 eval-large-scale.tex
typos and moving discussion section before related work
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@874 df1a90cd-247b-4364-bdaf-287a704eb499

The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, for both physical limits algorithms and dynamic limits algorithm show exactly the same trend as in small-scale evaluations, but with larger variations of minimum and maximum instantaneous satisfaction rates.

@@

At the same time, the probabilistic method completely failed to provide an adequate protection against the flooding attack, and in addition degraded service for the legitimate users after the attack finished.
The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
If the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.

>>>>

The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that for both physical limits algorithms and dynamic limits algorithm the performance is about the same as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.

@@

At the same time, the probabilistic method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
That is, if the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.
